Raft Distributed Consensus Algorithm over\\ WebRTC (Web Real-Time Communication)

### 2015-12-13 research_class/paper.tex
paper.tex: update abstract.
- Also, remove paper-min.tex intermediate file.

\begin{abstract}
We describe the creation of a browser-based distributed peer-to-peer
application using WebRTC, PeerJS and Raft.js. WebRTC is a protocol
that modern browsers have begun to integrate which enables
browser-to-browser communication. PeerJS is a WebRTC client library
and extensible signaling server. Raft.js is an implementation in
JavaScript of the Raft distributed consensus protocol. These
technologies are combined to create a chat application that guarantees
a shared, consistent and linearized view of the chat history without
relying on a single centralized server for communication. We also
create a series of automated tests using the SlimerJS browser
automation tool and use them to show the correctness of the chat
application and also to measure the performance and scalability of the
application for various cluster sizes.
\end{abstract}

>>>>

\begin{abstract}
We describe a browser-based middleware system for
creating distributed peer-to-peer applications. The system integrates
Raft.js, an implementation of the Raft distributed consensus
algorithm, with the WebRTC communication protocol which enables direct
browser-to-browser communication. The middleware system is used to
create a chat application that guarantees a shared, consistent and
linearized view of the chat history without relying on a single
centralized server for communication. The Raft over WebRTC middleware
and the chat application are validated with a series of automated
tests using the SlimerJS browser automation tool. The results
demonstrate the correctness and robustness of the system and also
characterize the system in terms of performance and scalability.
\end{abstract}
